Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Cleanup

Now  we discuss the general online
model where the request sequence
can be arbitrary.
In Section~\ref{sec:k3}, we show that the classic \emph{rent-or-buy} approach~\cite{karlin-ski-rental} provides an optimal algorithm for $k=3$.
We showed a lower bound of $\Omega(k \cdot \ell)$ that holds for $k=3$ (cf. Section~\ref{sec:lowerbound}), hence the result from this section is asymptotically optimal.

Then, in Section~\ref{sec:k2}, we show a strictly $6$-competitive algorithm for $k=2$.
\maciek{Intro: compare to previous 7-competitive algorithm. Note strict competitive ratio vs large additive term. Also, emphasize that the algorithm is different than 7-competitive}

\subsection{An Optimal Algorithm for Clusters of Size $3$}
\label{sec:k3}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\textwidth]{figs/substitute}
	\caption{Cluster types used in the analysis of \TAlg.}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\textwidth]{figs/substitute}
	\caption{an unsaturated edge that is inside a component}
\end{figure}

>>>>

Now  we discuss the general online
model where the request sequence
can be arbitrary.
In Section~\ref{sec:k3}, we show that the classic \emph{rent-or-buy} approach~\cite{karlin-ski-rental} provides an optimal algorithm for $k=3$.
We showed a lower bound of $\Omega(k \cdot \ell)$ that holds for $k=3$ (cf. Section~\ref{sec:lowerbound}), hence the result from this section is asymptotically optimal.
Furthermore, in Section~\ref{sec:k2}, we show a strictly $6$-competitive algorithm for $k=2$.

\subsection{An Optimal Algorithm for Clusters of Size 3}
\label{sec:k3}

@@

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.3\textwidth]{figs/substitute}
%	\caption{Cluster types used in the analysis of \TAlg.}
%\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\textwidth]{figs/substitute}
	\caption{an unsaturated edge that is inside a component. If there is a space next to it, maybe cluster types should fit next to it? Not sure.}
\end{figure}
